References

### 2017-07-10 cv/20sec/XieXiaolei.tex
Modified the CV and the paper with jeff.

% Skill bar section, each skill must have a value between 0 an 6 (float)
\skills {{Java/3},{Python/3},{SQL/4},{Matlab/5.2},{GNU Scientific Library/5},{R/5.8},{Parallel Computing OpenMP/4.5},{C/5},{C++/5}}

@@

\begin{itemize}
\item {\bf Xie, X.}, Davis, R.A., Heiny, J. and Mikosch, T.
  2016. {\it Extreme value analysis for the sample autocovariance
    matrices of heavy-tailed multivariate time series}.
  \underline{Extremes}, 19(3), pp.517-547.

@@

\item {\bf Xie, X}, Jan\ss en, A., Mikosch, T. and Rezapour, M.
  2016. {\it The eigenvalues of the sample covariance matrix of a
    multivariate heavy-tailed stochastic volatility model}.
  To appear in the \underline{Bernoulli Journal}.

@@

\section{Papers under Review}
\begin{itemize}
\item {\bf Xie, X.}, Mikosch, T. and de Vries, C., 2017,
  {\it Tail-indices and scale parameters of returns series}

@@

\section{Papers under Review}
\begin{itemize}
\item {\bf Xie, X.} Collamore, J, 2017
  {\it An efficient estimator of the probability of very large losses posed by
    GARCH(p,q) processes}

>>>>

% Skill bar section, each skill must have a value between 0 an 6 (float)
\skills {{Java/3},{Python/3},{SQL/4.5},{Matlab/4},{GNU Scientific Library/4},{R/4},{Parallel Computing OpenMP/3.8},{C/4.3},{C++/4.3}}

@@

\begin{itemize}
\item Davis, R.A., Heiny, J., Mikosch, T., {\bf Xie, X.},
  2016. {\it Extreme value analysis for the sample autocovariance
    matrices of heavy-tailed multivariate time series}.
  \underline{Extremes}, 19(3), pp.517-547.

@@

\item Jan\ss en, A., Mikosch, T., Rezapour, M., {\bf Xie, X},
  2016. {\it The eigenvalues of the sample covariance matrix of a
    multivariate heavy-tailed stochastic volatility model}.
  To appear in the \underline{Bernoulli Journal}.

@@

\section{Papers in Finalization}
\begin{itemize}
\item Mikosch, T., de Vries, C., {\bf Xie, X.}, 2017,
  {\it Tail-indices and scale parameters of returns series}

@@

\section{Papers in Finalization}
\begin{itemize}
\item Collamore, J., {\bf Xie, X.}, 2017
  {\it An efficient estimator of the probability of very large losses
    posed by GARCH(p,q) processes}
